%Full waveform inversion (FWI) aims to reconstruct subsurface properties from observed seismic data.
%Since FWI is an ill-posed inverse problem, appropriate regularizations or constraints are effective approaches to achieve accurate reconstruction.
%The total variation (TV) -type regularization or constraint is widely known as a powerful prior that models the piecewise smoothness of subsurface properties.
%However, the optimization problem of the TV-type regularized or constrained FWI is difficult to solve due to the nonlinearity of the observation process and the non-smoothness of the TV-type regularization or constraint.
%Conventional approaches to solve the FWI problem rely on inner loops and/or approximations, resulting in high computational cost and/or inappropriate solutions.
%In this paper, we develop an efficient algorithm with neither inner loops nor approximations to solve the FWI problem based on a primal-dual splitting method.
%We also demonstrate the effectiveness of the proposed method through experiments using the SEG/EAGE Salt and Overthrust Models.
Full waveform inversion (FWI) is a powerful technique for reconstructing subsurface properties from observed seismic data.
However, FWI is an ill-posed inverse problem, and it is effective to incorporate suitable regularizations or constraints to achieve stable and accurate reconstruction.
The total variation (TV)-type regularization or constraint is widely known as a powerful prior that models the piecewise smoothness of subsurface properties.
Despite its advantages, the integration of TV priors introduces significant computational challenges due to the nonlinearity of the observation process and the non-smoothness of the TV-type regularization or constraint.
Conventional approaches often rely on inner loops and/or approximations, leading to high computational cost and/or potentially inappropriate solutions.
In this paper, we develop an efficient algorithm for solving the TV-constrained FWI problem using a primal-dual splitting method.
The proposed approach eliminates the reliance on the need for inner loops and approximations, enhancing computational efficiency and reconstruction accuracy.
Numerical experiments on the SEG/EAGE Salt and Overthrust Models validate the performance of the proposed method and demonstrate its effectiveness in terms of both efficiency and accuracy.



